\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Charred green beans with anchovy dressing and dukkah}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

For the main dish:

\begin{itemize}
  \item $ \qty{300}{\gram} $ green beans, trimmed
  \item $ \qty{10}{\gram} $ basil
  \item $ 1 $ teaspoon oregano
\end{itemize}

For the anchovy dressing:

\begin{itemize}
  \item $ \qty{30}{\ml} $ olive old
  \item $ 3 $ anchovies
  \item $ 2 $ garlic cloves, crushed
  \item pinch of oregano
\end{itemize}

\columnbreak{}

For the pickled chillies:

\begin{itemize}
  \item $ 1 $ red chilli, thinly sliced
  \item $ 2 $ limes, squeezed
  \item $ \frac{1}{2} $ teaspoon, sugar
  \item $ \frac{1}{2} $ teaspoon, salt
\end{itemize}

For final seasoning:

\begin{itemize}
  \item $ 1 $ tablespoon Dukkah
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item First make the anchovy dressing. Place a small frying pan on medium high heat with the oil, garlic, anchovy and oregano. Cook for 2-3 minutes until the anchovies have broken down and the garlic is smelling fragrant. Set aside to cool.
  \item To make the pickled chillies, place the chillies, lemon juice, sugar and salt in a small bowl. Mix well and set aside to pickle while you get on with the rest.
  \item To assemble, spoon in 2 tbsp of the chilli pickling liquid into the anchovy dressing and mix well.
  \item Arrange some of the beans on a lipped platter with some of the picked herbs. Spoon over some of the anchovy dressing and pickled chillies, Sprinkle over some of the dukkah with the herbs and continue in a similar manner until all of the ingredients have been used up.
  \item Serve warm or at room temperature.
\end{enumerate}

\href{https://ottolenghi.co.uk/pages/recipes/charred-green-beans-with-anchovy-dressing-and-seed-dukkah}{Recipe from ottolenghi.co.uk}

\end{document}
