\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Cauliflower With Whole Spices}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 1 $ medium cauliflower, cut into $ \qty{2}{\cm} $ pieces
  \item $ 5 $ tablespoons vegetable oil
  \item $ 1 $ teaspoon whole cumin seeds
  \item $ 1 $ teaspoon whole coriander seeds
  \item $ 1 $ teaspoon black caraway seeds
  \item $ 1 $ dried chilli, chopped
\end{itemize}

\columnbreak{}

\begin{itemize}
  \item $ 6 $ cloves garlic, chopped
  \item $ 2 $ teaspoons ground coriander
  \item $ 2 $ teaspoons ground cumin
  \item $ \frac{1}{2} $ teaspoon ground turmeric
  \item $ 1 $ teaspoon salt
  \item $ \frac{1}{4} $ teaspoon cayenne pepper
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Heat oil in a frying pan.
  \item When hot, add the whole cumin, coriander, caraway and chilli.
  \item Lower heat to medium and put in the garlic and onion.
  \item Stir and fry for about $ \qty{5}{\min} $ minutes or until onions and garlic are lightly brown.
  \item Add cauliflower, ground coriander, cumin and turmeric. Stir to mix.
  \item Put in $ \frac{1}{4} $ cup ($ \qty{60}{\ml} $) water and bring to a simmer.
  \item Cover tightly and steam cauliflower over a very low heat for $ \qty{10}{\min} $ or until tender.
  \item Stir every $ \qty{3}{\min} $, replacing the lid each time.
  \item Boil any remaining liquid so the cauliflower has a \textit{dry} look.
\end{enumerate}

\href{https://www.masterclass.com/articles/indian-cauliflower-recipe-by-madhur-jaffrey}{Madhur Jaffrey's Cauliflower and Potatoes Recipe}

\end{document}
