\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Spanish Style Chicken \& Vegetable Bake}

\begin{document}

This is my variation of
\href{https://www.totalwellbeingdiet.com/au/recipes/quick-easy-recipes/spanish-style-chicken-vegetable-tray-bake/}{CSIRO
Total Wellbeing Diet} recipe. Instead of tinned tomatoes, I use fresh. To
increase the liquid, I make a tomato sauce. Brussels sprouts can be added, as
they absorb the tasty liquid and are marvellous when baked. Instead of white
wine, you can also use sake, gin or vodka.

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 2 $ teaspoons smoked paprika
  \item $ 2 $ teaspoons ground cumin
  \item olive oil
  \item $ 1 $ cup sweet white wine (or sake, gin or vodka also works)
  \item $ \frac {1}{3} $ cup lime juice
  \item $ 1 $ tablespoon tomato paste
  \item $ 1 $ lemon, cut into wedges, to serve
  \item $ 2 $ tablespoons parsley, chopped, to serve
  \item $ 1 $ chopped chilli (optional)
\end{itemize}

\columnbreak

\begin{itemize}
  \item $ 1 $ red onion, peeled, cut into rounds
  \item $ 1 $ bunch broccolini (Brussels sprouts can also be added)
  \item $ 4 $ mini coloured capsicums, chopped
  \item $ 1 $ garlic clove, thinly sliced
  \item $ \qty{300}{\gram} $ chicken thighs, skin off
  \item $ \qty{400}{\gram} $ cherry tomatoes
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Preheat oven to $ \qty{200}{\celsius} $.
  \item Scatter the onion, broccolini, capsicum, and garlic in a roasting pan.
  Spoon over $ 1 \frac {1}{2} $ teaspoons of oil. Sprinkle with half the paprika
  and half the cumin, then turn to coat. Roast for 15 minutes, turning once.
  \item Meanwhile, cut the chicken in half lengthways so you have thinner
  fillets. Brush both sides with the remaining oil. Combine the remaining
  paprika and cumin and sprinkle over both sides of the chicken, pressing in
  with your fingertips. (Optional: add a little sake to the marinade.)
  \item Heat a non-stick frying pan over medium-high heat. Add the chicken and
  cook on each side until sealed and golden.
  \item Combine the tomato paste, lime juice, and wine to make the tomato sauce.
  \item Remove the vegetables from the oven. Stir in the cherry tomatoes.
  Arrange the chicken over the vegetables. Add the tomato sauce. Return to the
  oven and cook for a further $ \qty{10}{\min} $, until the chicken is cooked
  through.
  \item Scatter over the parsley. Serve with lime wedges.
\end{enumerate}

\end{document}
