% vim: set filetype=plaintex shiftwidth=2 tabstop=2 expandtab:
\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures, see https://texdoc.org/serve/siunitx/0
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Salmon with Tomato}

\begin{document}

\subsection*{Ingredients}

\begin{itemize}
  \item Smoked Salmon, skin on
  \item Fresh garlic, chopped
  \item Capers
  \item 1 Orange (juice and zest)
  \item Cherry tomatoes
  \item Spinach
  \item Fresh chilli, chopped
  \item Olive oil
  \item Sea salt \& black pepper
\end{itemize}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Cook pasta according to packet instructions, drain and set aside.
  \item Separate the skin from the smoked salmon and cut into strips.
  \item Cut the salmon into pieces and set aside.
  \item Heat olive oil in a pan, over medium heat.
  \item Once the oil is hot, add the cherry tomatoes and salmon skin and cook until they begin to blister.
  \item Add garlic, capers, chilli, and orange zest and saut\'{e} until cooked, being careful that the garlic doesn't burn.
  \item Once cooked through, add orange juice and sea salt, stir to mix well.
  \item Add $\frac {3} {4}$ of the spinach and stir to combine.
  \item Add the smoked salmon and stir to combine.
  \item Add the cooked pasta and stir to combine.
  \item Serve over the remaining spinach.
  \item Shave parmesan over the top with cracked pepper.
\end{enumerate}

\href{https://kalejunkie.com/quick-easy-salmon-with-tomato-lemon-sauce/}{Based on Kale's Salmon with Tomato Saucerecipe}

\end{document}
