\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Orange and Soy Salmon Parcels}
\begin{document}

This is my variant of the original
\href{https://www.womensweeklyfood.com.au/}{Women's Weekly} recipe. You can
substitute lemon or lime for the orange. Instead of shallots you can also use
spring onions.

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 4 \times \qty{200}{\gram} $ salmon fillets
  \item $ 4 $ shallots, sliced thinly
  \item $ 1 $ piece fresh ginger, sliced thinly
  \item $ 2 $ cloves garlic, sliced thinly
  \item $ \qty{60}{\ml} $ light soy sauce
  \item $ 1 $ tablespoon finely grated orange/lemon rind
  \item $ \qty{80}{\ml} $ orange/lemon juice
  \item $ 2 $ teaspoons grated palm sugar
\end{itemize}

\columnbreak{}

\begin{itemize}
  \item $ \qty{450}{\gram} $ baby bok choy, chopped coarsely
  \item $ \qty{350}{\gram} $ broccolini, halved crossways
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Place each fillet on a piece of lightly oiled foil large enough to
  completely enclose fish. Combine onion, ginger, garlic, sauce, rind,
  juice and sugar in a small jug; divide mixture among fish pieces.
  Gather corners of foil above fish; twist to enclose securely.
  
  \item Cook parcels on a heated oiled grill plate (or grill or barbecue) for
  about 5 minutes or until the fish is cooked as desired.
  
  \item Meanwhile, boil, steam or microwave bok choy and broccolini,
  separately, until tender; drain. Serve salmon with vegetables.
\end{enumerate}

\href{https://www.womensweeklyfood.com.au/recipe/baking/orange-and-soy-salmon-parcels-7769/}{Orange and soy salmon parcels}

\end{document}
