% vim: set filetype=plaintex shiftwidth=2 tabstop=2 expandtab:
\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures, see https://texdoc.org/serve/siunitx/0
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Trinidad Curried Stew Fish}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\textbf{For washing the fish}

\begin{itemize}
  \item $ \qty{900}{\gram}$ fish (red snapper or flat head)
  \item $ 2 $ teaspoons salt
  \item $ 1 $ tablespoon lemon juice
\end{itemize}

\textbf{For marinating the fish}

\begin{itemize}
  \item salt
  \item freshly ground pepper
  \item $ 5 $ shallots, peeled \& diced
  \item $ 3 $ cloves garlic, peeled \& chopped
  \item $ \frac{1}{2} $ teaspoon ground turmeric
  \item $ 1 $ tablespoon lemon juice
\end{itemize}

\columnbreak{}

\textbf{For the curry sauce}

\begin{itemize}
  \item $ 3 $ tablespoons peanut or olive oil
  \item $ 1 $ medium onion, finely chopped
  \item $ 2 $ cloves garlic, finely chopped
  \item $ 2 $ hot chillies, chopped
  \item $ 4 $ teaspoons hot curry powder
  \item $ \qty{300}{\ml} $ tomatoes, grated
  \item $ \qty{400}{\ml} $ vegetable stock
  \item $ \frac{1}{2} $ teaspoon salt
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Wash fish. Rub with salt and lemon juice. Rinse with cold water. Put
  into a baking dish. Set aside.
  \item Put the onions, garlic, pepper, turmeric and lemon juice and $
  \frac{1}{2} $ teaspoon salt and $ 2 $ tablespoons water into a blender. Blend
  into a smooth paste.
  \item Rub the paste over the fish and marinate for $ \qty{30}{\min} $.
  \item Make the curry sauce. Heat the oil in a wide lidded pan and set over a
  medium-high heat. When hot, add the onions, garlic and chillies. Fry until
  onions begin to brown. Stir in the curry powder. Add tomatoes, stock and salt.
  Stir and bring to the boil. Cover, reduce the heat to low and cook gently for
  $ \qty{30}{\min} $.
  \item Preheat the oven to $ \qty{180}{\celsius} $.
  \item Pour the sauce over the marinated fish, cover the dish with foil and
  bake in the oven for $ \qty{30}{\min} $.
\end{enumerate}

Madhur Jaffrey's Ultimate Curry Bible, Trinidad, Birdie's Curried Stew Fish

\end{document}
