\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures, see https://texdoc.org/serve/siunitx/0
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Grilled Fish with Sri Lankan Tomato-Coriander Curry Paste}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ \qty{450}{\gram} $ haddock, cod, salmon or barramundi
  \item $ \frac{1}{2} $ teaspoon ground turmeric
  \item $ 5 $ tablespoons peanut or olive oil
  \item $ 1 $ small cinnamon stick
  \item $ 2 $ cardamon pods
  \item $ 1 $ medium onion, sliced in thin half-rings
  \item $ 2 $ cloves garlic, crushed
\end{itemize}

\columnbreak{}

\begin{itemize}
  \item $ 1 $ teaspoon ground fennel
  \item $ 1 $ teaspoon ground coriander
  \item $ \frac{3}{4} $ teaspoon cayenne pepper
  \item $ 3 $ medium tomatoes, finely chopped
  \item $ \qty{30}{\gram} $ fresh coriander, finely chopped
  \item $ 1 $ tablespoon Dijon mustard
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\subsection*{Fish Marinade}

\begin{itemize}
  \item Lightly dust the fish with salt and half of the ground turmeric. 
  \item Cover and set aside in the fridge.
\end{itemize}
  
\subsection*{Fish Marinade}

\begin{enumerate}
  \item Pour $ 3 $ tablespoons oil into a large, lidded pan, and set on medium high heat. When the oil is hot, put in the cinnamon and cardamon.
  \item Shortly after put in the onion and garlic. Stir and fry until onions start to brown.
  \item Add the fennel, ground coriander, cayenne pepper and remaining turmeric. Stir once.
  \item Add the tomatoes, chopped coriander and $ \frac {1}{2} $ teaspoon salt and $ \qty{250}{\ml} $ water. Bring to the boil, cover, reduce heat to low and simmer gently for $ \qty{15}{min} $.
  \item Stir in the mustard. Turn off the heat.
  \item Just before serving, add the fish and gently poach for $ \qty{5}{min} $.
\end{enumerate}

\href{https://www.eatyourbooks.com/library/recipes/423431/grilled-fish-in-a-sri}{Grilled Fish in a Sri Lankan Tomato-Coriander Curry Sauce by Madhur Jaffrey}

\end{document}
