\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Phil's Lentil Soup}

\begin{document}

\paragraph*{}
This is a Pakistani Dhal recipe I first tasted at Phil's in 2024.


\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 2 \frac{1}{2} $ cups red lentils, soaked and rinsed
  \item $ 2 $ medium onions, finely diced
  \item $ 3 $ cloves garlic, finely diced
  \item $ 1 $ teaspoon chopped ginger
  \item $ 1 $ teaspoon freshly ground cloves
  \item $ 1 $ red chilli, chopped
  \item $ 1 $ teaspoon salt
  \item $ 1 \frac{1}{2} $ teaspoons ground coriander
  \item $ \frac{1}{2} $ teaspoon ground cumin
  \item $ 1 $ teaspoon turmeric
  \item $ 2 $ large tomatos, skin removed
\end{itemize}

\columnbreak

Use the following to finish the soup:

\begin{itemize}
  \item $ 3 $ tablespoons butter
  \item $ 6 $ cloves garlic, finely chopped
  \item $ 1 $ teaspoon paprika
  \item $ 1 $ teaspoon cumin seeds
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Soak lentils 2 hours in 4 cups water, drain and wash.
  \item Heat oil in a large pot, hot add cloves, chilli. Saute for 2 minutes.
  \item Add onions, garlic and ginger and fry until onions browned.
  \item Reduce heat. Then add coriander, cumin, turmeric and fry for 2 minutes.
  \item Add tomatoes.
  \item Add lentils and 5 cups of cold water.
  \item Cook for $1 \frac {1}{2}$ hours on a low heat until lentils are soft.
\end{enumerate}

Finish with:

\begin{enumerate}
  \item Add butter to a saucepan on a high heat.
  \item Add garlic, cumin, paprika and a pinch of salt.
  \item Once melted in, stip and turn down heat for a minute more.
  \item Pour on top of dhal and swirl with a spoon. Don't mix it in.
  \item Stand the soup with the finish for 10 minutes before serving.
\end{enumerate}

\end{document}
