\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Moroccan Spiced Fish with Roasted Cauliflower \& Pickled Cucumber Salad}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 3 $ tablespoons white wine vinegar
  \item $ 1 $ tablespoon brown sugar
  \item salt \& black pepper
  \item $ 1 \frac{1}{2} $ teaspoons Moroccan seasoning
  \item olive oil, sprayed
\end{itemize}

\columnbreak

\begin{itemize}
  \item $ 300 $ \si{\gram} white fish fillets (e.g., flathead, gurnard)
  \item $ 2 $ unpeeled, sliced cucumbers
  \item $ \frac {1}{2} $ cauliflower, pieces
  \item $ 1 $ red onions, thinly sliced (use grater)
  \item $ 1 $ medium tomato, chopped
  \item $ 1 $ cup baby spinach or baby rocket
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item For the quick pickled cucumber salad, in a bowl, combine vinegar, sugar and $\frac {1}{4}$ teaspoon of salt, stir until sugar has dissolved. Season and add cucumber and onion. Stir to coat. Cover and set aside.
  \item Meanwhile, place a roasting pan in the oven and preheat the oven and pan to 210\si{\celsius} fan-forced. Spray cauliflower with oil. Sprinkle 1 tablespoon of Moroccan seasoning over cauliflower and turn to coat. Place cauliflower onto the hot pan and roast for 10 minutes.
  \item Spray both sides of the fish with oil and sprinkle over the remaining seasoning. Remove cauliflower from the oven, turn cauliflower over and add the fish to the pan. Roast for a further 15 minutes, or until the fish is cooked through.
  \item Drain the pickled cucumber and onion and return to the bowl. Add the tomato and rocket/spinach and toss to combine.
  \item Divide the fish and cauliflower between two serving plates. Serve with the salad.
\end{enumerate}

Serves 2

\href{https://www.totalwellbeingdiet.com/au/recipes/healthy-summer-recipes/moroccan-spiced-fish-with-roasted-cauliflower-pickled-cucumber-salad/}{CSIRO Total Wellbeing Diet}

\end{document}
