\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Dry Potatos with Mustard Seeds}

\begin{document}

\subsection*{Ingredients}

\begin{itemize}
  \item $ 4 $ medium-sized boiling potatoes, the waxier the better
  \item $ 6 $ tablespoon vegetable oil
  \item $ 1 $ clove garlic, crushed
  \item $ 1 $ shallot, diced
  \item $ 1 $ tablespoon black mustard seeds
  \item $ \frac{1}{2} $ teaspoon ground turmeric
  \item $ \frac{1}{2} $ teaspoon salt
  \item $ \frac{1}{4} $ teaspoon cayenne pepper
\end{itemize}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Peel and dice potatoes into $ \qty{2}{\centi\metre} $ pieces. Put into
  a bowl of water and drain just before you start to cook.
  \item Heat the oil in a pan over a medium heat. Add the mustard seeds. As
  they start to pop, add the garlic, shallot. Stir in the turmeric.
  \item Add the drained potatoes, stir for $ \qty{1}{\minute} $.
  \item Cover the potatoes and turn to low. Cook covered for $
  \qty{30}{\minute} $ or until potatoes are cooked through but retain their
  shape. 
  \item Stir gently every $ \qty{5}{\minute} $ to $ \qty{7}{\minute} $.
  \item When the potatoes are cooked, sprinkle with salt and cayenne. Stir
  again to mix.
\end{enumerate}

\href{https://ivu.org/legacy-recipes/indian-root/dry-j.html}{Madhur Jaffrey - Eastern Vegetarian Cooking}

\end{document}
