\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Shepherd's Pie}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}




\begin{itemize}
  \item $ 1 $ tablespoon olive oil
  \item $ 1 $ brown onion, halved, finely chopped
  \item $ 1 $ carrot, peeled, finely chopped
  \item $ 2 $ celery sticks, trimmed, finely chopped
  \item $ 1 $ tablespoon tomato paste
  \item $ 4 $ desiree potatoes, peeled, chopped
\end{itemize}

\columnbreak

\begin{itemize}
  \item salt \& black pepper
  \item $ 2 $ tablespoons plain flour
  \item $ 500 $ \si{\milli\litre} ($ 2 $ cups) beef style stock
  \item $ 1 $ tablespoon Worcestershire sauce
  \item $ 1 $ bay leaf
  \item $ 40 $ \si{\gram} butter
  \item $ 125 $ \si{\milli\litre} ($ \frac{1}{2} $ cup) milk
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Heat oil in a large saucepan over medium-high heat. Add onion, carrot and celery and cook, stirring, for 5 minutes or until soft. Add mince and cook, stirring to break up any lumps, for 5 minutes or until meat changes colour.
  \item Add the flour and cook, stirring, for 2 minutes or until combined. Add stock beef, bay leaf, Worcestershire sauce and tomato paste. Bring to the boil. Reduce heat to low and cook, stirring occasionally, for 30 minutes or until sauce thickens. Taste and season with salt and pepper.
  \item Meanwhile: cook potatoes desiree potatoes in a saucepan of salted boiling water for 15 minutes or until tender. Drain well. Return to the pan with the butter. Use a potato masher or fork to mash until smooth. Add milk and use a wooden spoon to stir until combined. Taste and season with salt and pepper.
  \item Preheat oven to 200\si{\celsius}. Spoon lamb mixture into a 2\si{\litre} (8-cup) capacity ovenproof baking dish, or use four individual oven proof serving dishes. Top with mashed potato and use a fork to spread over lamb mixture. Add grated cheese on top. Bake in a preheated oven for 20 minutes or until mashed potato is golden brown.
\end{enumerate}

\end{document}
