\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Spanish Style Chicken \& Vegetable Bake}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 2 $ teaspoons smoled paprika
  \item $ 2 $ teaspoons ground cumin
  \item $ 1 $ lemon, wedges, to serve
  \item $ 2 $ tablespoons parsley, chopped, to serve
  \item olive oil
\end{itemize}

\columnbreak

\begin{itemize}
  \item $ 1 $ red onion, peeled, cut into rounds
  \item $ 1 $ bunch broccolini
  \item $ 4 $ mini, coloured capsicums, chopped
  \item $ 1 $ garlic clove, thinly sliced
  \item $ \qty{300}{\gram} $ chicken breast, skin off
  \item $ \qty{400}{\gram} $ tin cherry tomatoes, in juice
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Pre-heat oven to $ \qty{200}{\celsius} $
  \item Scatter the onion, broccolini, capsicum and garlic in a roasting pan. Spoon over $ 1 \frac {1}{2} $ teaspoons of oil. Sprinkle with half the paprika and half the cumin, turn to coat. Roast for 15 minutes, turning once.
  \item Meanwhile, cut the chicken in half lengthways so you have 2 thinner fillets. Brush both sides with remaining $ \frac{1}{2} $ teaspoon of oil. Combine the remaining paprika and cumin and sprinkle over both sides of the chicken, pressing on with your fingertips.
  \item Heat a non-stick frying pan over medium to high heat. Add chicken, cook for 30 seconds each side, or until golden.
  \item Remove the vegetables from the oven. Stir in the cherry tomatoes. Arrange the chicken over the vegetables. Return to the oven, cook for 8 minutes until chicken is cooked through.
  \item Scatter over the parsley if using. Serve with lemon wedges.
\end{enumerate}

\href{https://www.totalwellbeingdiet.com/au/recipes/quick-easy-recipes/spanish-style-chicken-vegetable-tray-bake/}{CSIRO Wellbeing Diet}

\end{document}
