\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures, see https://texdoc.org/serve/siunitx/0
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Hyderabadi Tomato Chutney}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ \qty{450}{\gram} $ ripe tomatoes, chopped
  \item $ 1 $ teaspoon ginger, finely grated
  \item $ 1 $ teaspoon garlic, mashed pulp
  \item $ \frac{1}{2} $ teaspoon turmeric, ground
  \item $ \frac{1}{4} $ teaspoon cayenne pepper
  \item $ 4 $ tablespoons vegetable oil
\end{itemize}

\columnbreak{}

\begin{itemize}
  \item $ 4 $ cloves garlic, peeled
  \item $ 1 $ teaspoon cummin seeds 
  \item $ \frac{1}{2} $ teaspoon black mustard seeds
  \item $ \frac{1}{4} $ teaspoon fenugreek seeds
  \item $ 2 $ dried red chillies, whole
  \item $ \frac{1}{2} $ teaspoon salt
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Put the tomatoes, ginger, garlic pulp, turmeric and cayenne in a bowl and mix.
  \item Heat oil in a frying fan over a medium heat.
  \item When hot, put in the cloves of garlic. Stir and fry until they are brown.
  \item Add cummin, mustard, fenugreek seeds. Let the sizzle for a couple of seconds.
  \item Put in the chillies, stir once. They should swell and turn dark red.
  \item Put in the tomato mixture. Stir and cook for 15 minutes or until tomatoes are fairly dry.
  \item Add the salt and mix in.
  \item Can be served hot or cold.
  \item Store in a jar in a refrigerator. It should last at least a week.
\end{enumerate}

\href{https://www.penguin.com.au/books/eastern-vegetarian-cooking-9780099777205}{World of East Vegetarian Cooking by Madhur Jaffrey}

\end{document}
