% vim: set filetype=plaintex shiftwidth=2 tabstop=2 expandtab:
\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures, see https://texdoc.org/serve/siunitx/0
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont White Oil Spray}

\begin{document}

\subsection*{Ingredients}

\begin{itemize}
  \item $ \qty{ 500 }{\ml} $ of vegetable oil (any brand)
  \item $ \frac{1}{2} $ cup Sunlight dish washing liquid
\end{itemize}

\subsection*{Method}

\begin{itemize}
  \item Combine all ingredients
  \item Store in a suitable container.
\end{itemize}

\subsection*{Dilution}

To use, first dilute mix by placing 1 tablespoon into a litre of water.
Mix well and spray thoroughly over both sides of the foliage and onto
the offending pest. The contents of the stored concentrate will separate
over time. Simply ensure that the concentrate is well mixed each time
before you attempt to dilute it for use. Spray as often as required.

\subsection*{Use}

Oil based sprays are useful in controlling a wide range of insect pests
and mites. In most cases the oil covers the body of the insect or mite,
causing it to suffocate. Scale, aphids, pimple psyllids, mites and even
young grasshoppers can be killed by contact with the oil. In the case of
citrus leaf miner, the shiny oil coating on the leaves repels the moth
responsible for laying eggs on the new leaves of citrus plants. These
eggs quickly hatch into larvae that tunnel between the upper and lower
surfaces of the leaves causing the characteristic silvery trails and
distortion of the leaves.

\subsection*{Precautions}

Always following the directions as to the dilution rate as oil-based
sprays can burn if applied in strong concentrations. Do not apply in hot
weather. Do not use on plants with hairy leaves, ferns or palms and
reduce to half strength on native plants with fine foliage (eg
leptospermums or tea trees). These precautions apply to home made
preparations as well as commercially available oil sprays. Commercially
available preparations are generally petroleum-based products and their
use is not permitted under organic certification.

\subsection*{Organic Sprays}


For Organic Sprays see \url{http://www.zerowaste.sa.gov.au/prog_garden.php}

\end{document}
